\name: Combining Bottom-up and top-down approaches through graph learning over interaction networks for drug-target-interaction prediction

### 2021-03-20 paper/main.tex
.

As we were quite surprised about the MacroAUC discrepancy between the splitting schemes, we evaluated other cutting edge drug--target interaction and drug--target affinity prediction methods, training and evaluating on other datasets. Following the results of MolTrans (\textbf{CITATION}), we reevaluated DeepDTI (\textbf{CITATION}), DeepDTA (\textbf{CITATION}), DeepConv-DTI (\textbf{CITATION}) and MolTrans itself on BioSnap (\textbf{CITATION}) over a protein split, as shown in part (d) of Table \ref{tab:Results}. The authors of MolTrans evaluated all considered methods over the drug--target pair and the protein split, which we were able to reproduce with (d), showing once more a substantial divergence. However, we additionally computed the $MicroAUC_p$ score for all considered methods, leading to comparable scores as for the Yamanishi evaluated methods.

>>>>

As the difference in performance with different splitting schemes is
quite striking, we evaluated additional drug--target interaction and
drug--target affinity prediction methods that were trained and
evaluation on other datasets.  Following the results of MolTrans
(\textbf{CITATION}), we reevaluated DeepDTI (\textbf{CITATION}),
DeepDTA (\textbf{CITATION}), DeepConv-DTI (\textbf{CITATION}) and
MolTrans itself on BioSnap\todo{What is that? Is it in methods?}
(\textbf{CITATION}) over a protein split, as shown in part (d) of
Table \ref{tab:Results}. The authors of MolTrans evaluated all
considered methods over the drug--target pair and the protein split;
we were able to reproduce the results (Table \ref{tab:Results} (d)),
showing a substantial difference based on the splitting scheme. We
additionally computed the $MicroAUC_p$ score for all considered
methods, leading to comparable\todo{are the datasets comparable?}
scores as for the results obtained on the Yamanishi dataset.
